### 2021-08-30 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/paper.tex
30.08.21.1

\begin{abstract}
Roaming is the capability of a subscriber to have persistence of service in a visited mobile network managed by a different operator. To achieve this persistence of connectivity it is necessary for operators to agree on technical, legal and commercial aspects in what is known as a Roaming Agreement. Currently, Roaming Agreement negotiation uses asynchronous flow such as email or even regular mail within the agreement drafting phase, which on the one hand do not ensure transparency and on the other hand constitute a waste of time with duration of up to one month. To address the lack of transparency and reduce wasted time, this paper proposes the use of a Natural Language Processing Engine as a starting point for the digitalization of the negotiation process towards a transparent drafting of Roaming Agreements. The Natural Language Processing Engine not only is designed but also is implemented and tested. Testing is performed as part of an experimentation phase to measure the accuracy at which the output file is populated regarding the original Roaming Agreement.
\end{abstract}

\begin{IEEEkeywords}
Natural Language Processing, Telecommunication, Roaming Agreement, Amazon Comprehend, Similarity
\end{IEEEkeywords}

\section{Introduction}
The roaming service maintains the persistent connectivity of subscribers in different networks and locations. Roaming describes the capability of a subscriber to access mobile services offered by the visited public mobile network (VPMN) through the home public mobile network (HPMN), when roaming outside the coverage range of the HPMN \cite{Tanaka2013}. However, before ensuring persistent connectivity in VPMN the Mobile Network Operators (MNOs) must reach an agreement regarding the technical, commercial and legal relationships known as the Roaming Agreement (RA). In this regard, it is possible to establish 3 stages within the RA: \textit{drafting}, \textit{testing} and \textit{implementation}.

In order to standardize technical, commercial and legal aspects of RA, the GSM Association broadly outlines the content of such RA in standardized form for its members \cite{Ferwerda2018}. Rocco \footnote{Rocco Group: https://www.rocco.group} provides a list of the most commonly used GSMA standards, which are summarized bellow \cite{ROCCO2017}: (1) AA.12 constitutes the permanent reference document; (2) AA.13 contains the common annexes with operational information (e.g., information on tap file, billing data, settlement procedure, customer care, fraud, etc.) and (3) AA.14 involves the individual annexes containing information about the operator (e.g., contact details of the roaming team, fraud team, IREG team, TADIG team, etc.).

While it is true that it is not mandatory to follow the standards proposed by GSMA, according to authoritative voices in the field of negotiating RA drafting, most MNOs follow them strictly \cite{ROCCO2017a}. Therefore, a first point to consider in the RA drafting is how far it is deviated from the GSMA's proposed standards. Thus, during the drafting process of the agreement, the parties should analyze the sub-articles contained in the GSMA standard templates to determine whether:

\begin{enumerate}
\item Specify the value of certain \textit{variables} that are found in a certain text, such as dates, names of MNOs, locations and others.

\item Leave an article/sub-article as found in the template thereby establishing a \textit{standard clause}.

\item Introduce certain \textit{variations} in the articles/sub-articles, by changing \textit{variables}, e.g., MNO commercial name, dates, penalties.

\item Introduce completely new articles/sub-articles that respond to particular interests by constituting \textit{customized texts}.

\end{enumerate}

However, the drafting of a RA goes through a complex negotiation process in which, at present, the parties, i.e. the MNOs, still use asynchronous flows such as e-mail or even regular mail for the information exchange. On the one hand, this process lacks transparency, which can lead to violation of the RA by MNOs. On the other hand, this process is a waste of time. As Rocco points out, the entire process can be to up 1 month, depending on the responsiveness of the MNOs \cite{ROCCO2017a}. Therefore, it is necessary to provide a transparent digitization system for RA drafting negotiations, which guarantees the use of a few days or even hours. For this reason, this paper proposes the use of Natural Language Processing (NLP) as a legal text digitization engine. This NLP Engine constitutes the starting point for the digitalization of the negotiation process towards a transparent drafting of Roaming Agreements. The NLP Engine analyzes articles and sub-articles of the RA determining the existence of variables, variations, standard clauses and customized texts. For this purpose, the NLP Engine relies on the one hand, on NLP techniques such as Named Entity Recognition (NER) and Part of Speech (POS) using the unstructured data information discovery tool \textit{Amazon Comprehend} and, on the other hand, by establishing an comprehensive comparison between texts based on \textit{similarity} determination techniques. The procedures for integrating tools, NLP techniques, pre-processing and post-processing constitute a methodological framework designed for the use case and included within an unstructured text processing tool. This article includes not only the design phase, but also the implementation and evaluation of the NLP Engine tool.

The rest of this manuscript is structured as follows: Section 2 analyzes the related work in order to determine the novelty of the proposed topic. Section 3 establishes the designed methodology. The implementation of our system are described in Section 4. Section 5 discusses the results of conducted experiments. Finally, the conclusions of the manuscript are included in Section 6.

@@

This section reviews both the attempts at transparent digitalization of roaming agreements and existing NLP techniques-based text processing systems.

Both in the scientific literature and in business environments there are important approaches to RA digitalization. Thus, the reference \cite{9369516} proposes a dynamic RA between the Local 5G Operator and the MNO. The interaction between the two entities takes place through an Ethereum based platform. A second approach focuses uniquely on the billing of the services obtained as a result of the RA \cite{9024541}. This agreement is incorporated as part of a chaincode of a Hyperledger Fabric Blockchain network so the work contributes significantly to the digitalization process of the RA, allowing for a faster, more seamless process in which payments can be requested and obtained quickly due to less need for manual intervention. The contextualization of this system in the business environment is proposed by important MNOs such as Telefonica, Deutsche Telekom and Vodafone which use blockchain for Roaming settlement within the framework of the RA between the parties \cite{Huillet2020}. Despite the value of these contributions from a RA implementation perspective, they are not within the context of a transparent digitalization to improve the negotiation process for the effective drafting of the roaming agreement.

>>>>

\begin{abstract}
Roaming is the capability of a subscriber to have persistence of service in a visited mobile network managed by a different operator. To achieve this persistence of connectivity it is necessary for operators to agree on technical, commercial and legal aspects in what is known as a Roaming Agreement. Currently, Roaming Agreement negotiation uses asynchronous flow such as email or even regular mail. 
The most important and affecting period within the roaming agreement is known as the drafting phase as it did not ensure transparency and it  is time consuming. To address the lack of transparency and reduce wasted time, this paper proposes a framework that automate the process of drafting the roaming agreement and enable better accessibility. The proposed framework exploits a Natural Language Processing Engine as a starting point for the digitalization of the negotiation process towards a transparent drafting of Roaming Agreements. Extensive experiments on real roaming agreements show the superiority of our proposed framework in drafting the roaming agreements against the traditional drafting negotiation process with prediction accuracy over 80.0\%.
% The Natural Language Processing Engine not only is designed but also is implemented and tested. Testing is performed as part of an experimentation phase to measure the accuracy at which the output file is populated regarding the original Roaming Agreement.
\end{abstract}

\begin{IEEEkeywords}
Roaming Agreement, Natural Language Processing, Telecommunication
\end{IEEEkeywords}

\section{Introduction}
The roaming service maintains the persistent connectivity of subscribers in different networks and locations. Roaming describes the capability of a subscriber to access mobile services offered by the visited public mobile network (VPMN) through the home public mobile network (HPMN), when roaming outside the coverage range of the HPMN \cite{Tanaka2013}. However, before ensuring persistent connectivity in VPMN the Mobile Network Operators (MNOs) must reach an agreement regarding the technical, commercial and legal relationships known as the Roaming Agreement (RA). In this regard, it is possible to establish three stages within the RA: \textit{drafting}, \textit{testing} and \textit{implementation}. The testing and implementation phases are straight forward as they are related with implementing what is agreed on the drafting phase. However, the drafting phase is ambiguous and needs a lot of efforts from both parties, i.e. the MNOs.

Therefore, in order to reduce the exerted efforts and standardize technical, commercial and legal aspects of the RA, the GSM Association broadly outlines the content of such RA in standardized form for its members \cite{Ferwerda2018}. 
In addition, many organizations attempt to unify RAs. For example, Rocco\footnote{Rocco Group: https://www.rocco.group}, which is a company specialized in telecommunication reports including roaming agreements, provides a list of the most commonly used GSMA standards. It summarizes these standards as follows \cite{ROCCO2017}: (1) AA.12 constitutes the permanent reference document; (2) AA.13 contains the common annexes with operational information (e.g., information on tap file, billing data, settlement procedure, customer care, fraud, etc.) and (3) AA.14 involves the individual annexes containing information about the operator (e.g., contact details of the roaming team, fraud team, IREG team, TADIG team, etc.).

While it is true that it is not mandatory to follow the standards proposed by the GSMA organization, according to authoritative voices in the field of negotiating RA drafting, most MNOs follow them strictly \cite{ROCCO2017a}. Therefore, the first point to consider in the RA drafting is how far it is deviated from the GSMA's proposed standards. Thus, during the drafting process of the agreement, the parties should analyze the sub-articles contained in the GSMA standard templates. This necessitates discretizing the bulk of the roaming agreement template and classifying each word/clause from an existing classes as follows:

\begin{enumerate}
\item Specify the value of certain \textit{variables} that are found in a certain text, such as dates, names of MNOs, locations and others.
\item Introduce certain \textit{variations} in the articles/sub-articles, by changing \textit{variables}, e.g., MNO commercial name, dates, penalties.
\item Leave an article/sub-article as found in the template (RA draft); thereby establishing a \textit{standard clause}.
\item Introduce completely new articles/sub-articles that respond to particular interests by constituting \textit{customized texts}.
\end{enumerate}

However, the \textit{drafting} of a RA goes through a complex negotiation process in which, at present, the parties still use asynchronous flows such as e-mail or even regular mail to exchange the information. Thus, this traditional negotiation process has multiple drawbacks including lacks of transparency, which can lead to violations of the RA by MNOs. In addition, this process is laborious and time consuming. As Rocco points out, the entire process can take up to one month, depending on the responsiveness of the MNOs \cite{ROCCO2017a}. Therefore, it is necessary to provide a transparent digitalization system for RA drafting negotiations, which guarantees transparency and shortening the negotiation time, which could be a couple of days or even hours. Hence, this work develops a framework that exploits the advancement in the Natural Language Processing (NLP) discipline and use it as a legal text digitalization engine. This NLP Engine constitutes the starting point for the digitalization of the negotiation process towards a transparent drafting of Roaming Agreements. The proposed NLP Engine analyzes articles and sub-articles of the RA by determining the existence of variables, variations, standard clauses and customized texts. To do so, the proposed NLP Engine relies on the advancement of NLP techniques such as Named Entity Recognition (NER) and Part of Speech (POS) in drafting RAs.

% using the unstructured data information discovery tool \textit{Amazon Comprehend} and, on the other hand, by establishing an comprehensive comparison between texts based on \textit{similarity} determination techniques. The procedures for integrating tools, NLP techniques, pre-processing and post-processing constitute a methodological framework designed for the use case and included within an unstructured text processing tool. This article includes not only the design phase, but also the implementation and evaluation of the NLP Engine tool.

% The rest of this manuscript is structured as follows: Section 2 presents the related work in order to determine the novelty of the proposed topic. Section 3 establishes the designed methodology. The implementation of our system are described in Section 4. Section 5 discusses the results of conducted experiments. Finally, the conclusions of the manuscript are included in Section 6.

@@

The existing work that is related to the roaming agreements can be categorized into two main categories. The first category encompasses the work, which focused on transparent digitalization of roaming agreements~\cite{9369516, 9024541, Huillet2020}, whereas the second category includes the work that apply existing NLP techniques-based text processing systems~\cite{8487847, 9138070, 9104105}.

Both in the scientific literature and in business environments there are important approaches to RA digitalization. Thus, the reference \cite{9369516} proposes a dynamic RA between the Local 5G Operator and the MNO. The interaction between the two entities takes place through an Ethereum based platform. Despite the contributions of this work in the roaming agreement implementation phase, the fact of performing the implementation on the Ethereum network implies that the transactions cost must be born among the participating MNOs. Additionally, although the authors justify the latency given that they repeated the experiment 100 times, the non-deterministic nature of the network implies that may suffer congestion anytime. A second approach focuses uniquely on the billing of the services obtained as a result of the RA \cite{9024541}. This agreement is incorporated as part of a chaincode of a Hyperledger Fabric Blockchain network so the work contributes significantly to the digitalization process of the RA, allowing for a faster, more seamless process in which payments can be requested and obtained quickly due to less need for manual intervention. The contextualization of this system in the business environment is proposed by important MNOs such as Telefonica, Deutsche Telekom and Vodafone which use blockchain for Roaming settlement within the framework of the RA between the parties \cite{Huillet2020}. Despite the value of these contributions from a RA implementation perspective, they are not within the context of a transparent digitalization to improve the negotiation process for the effective drafting of the roaming agreement.
